% Reproduction of LLMs survey tree (IMG_6736.JPG)
% Compile with: pdflatex llms-survey.tex
\documentclass[border=8pt]{standalone}
\usepackage[T1]{fontenc}
\usepackage{forest}
\usepackage{xcolor}

% Colors sampled from the source image (light blue leaves, gray box borders)
\definecolor{leaffill}{RGB}{220, 233, 245}      % pale blue citation leaves
\definecolor{leafborder}{RGB}{120, 165, 210}    % muted blue border for leaves
\definecolor{boxborder}{RGB}{120, 120, 120}     % gray border for category boxes

\tikzset{
  rootbox/.style={
    draw=boxborder, rounded corners=3pt,
    text width=1.7cm, align=center,
    font=\footnotesize, inner sep=4pt, minimum height=8mm,
  },
  l1box/.style={
    draw=boxborder, rounded corners=3pt,
    text width=3.0cm, align=center,
    font=\footnotesize, inner sep=4pt, minimum height=6mm,
  },
  catbox/.style={
    draw=boxborder, rounded corners=3pt,
    text width=2.8cm, align=center,
    font=\footnotesize, inner sep=4pt, minimum height=6mm,
  },
  leafbox/.style={
    draw=leafborder, line width=0.4pt, fill=leaffill,
    rounded corners=3pt,
    text width=4.6cm, align=left,
    font=\scriptsize, inner sep=4pt,
  },
}

\begin{document}
\begin{forest}
  for tree={
    grow'=east,
    parent anchor=east, child anchor=west,
    l sep=12pt, s sep=5pt,
    edge={-, thin, draw=boxborder},
    edge path={
      \noexpand\path[\forestoption{edge}, rounded corners=3pt]
        (!u.parent anchor) -- +(6pt,0) |- (.child anchor);
    },
  },
  where level=0{rootbox}{},
  where level=1{l1box}{},
  where level=2{catbox}{},
  where n children=0{leafbox}{},
  [{LLMs\\\lbrack70--73\rbrack}
    [{\textbf{Fundamental Problems}}
      [{Supervised Fine-tuning}
        [{Zhang et al. [8].}]
      ]
      [{Alignment}
        [{Shen et al. [9], Wang et al. [10], Liu et al. [11].}]
      ]
      [{Retrieval Augmentation}
        [{Gao et al. [12].}]
      ]
      [{Knowledge Editing}
        [{Wang et al. [13], Yao et al. [14], Wang et al. [15], Feng et al. [16], Zhang et al. [17].}]
      ]
      [{Tool Usage}
        [{Qin et al. [18].}]
      ]
      [{Long-context}
        [{Huang et al. [19], Wang et al. [20], Pawar et al. [21].}]
      ]
      [{Multimodal}
        [{Wu et al. [22], Song et al. [23], Caffagni et al. [24], Yin et al. [25].}]
      ]
      [{Efficiency}
        [{Bai et al. [26], Wan et al. [27], Miao et al. [28, 28], Xu et al. [29], Zhu et al. [30], Xu and McAuley [31], Wang et al. [32], Park et al. [33].}]
      ]
    ]
    [{\textbf{Evaluation}}
      [{Chang et al. [34], Guo et al. [35].}]
    ]
    [{\textbf{Applications}}
      [{Information Processing}
        [{Yang et al. [36], Zhu et al. [37], Xu et al. [38].}]
      ]
      [{Software Engineering}
        [{Fan et al. [39], Wang et al. [40], Zheng et al. [41].}]
      ]
      [{Robotics}
        [{Zeng et al. [42].}]
      ]
      [{Autonomous Driving}
        [{Cui et al. [43], Yang et al. [44].}]
      ]
      [{Medecine}
        [{He et al. [45], Zhou et al. [46], Wang et al. [47].}]
      ]
      [{Finance}
        [{Li et al. [48].}]
      ]
      [{Psychology}
        [{He et al. [49].}]
      ]
      [{Recommendation}
        [{Li et al. [50], Lin et al. [51], Wang et al. [52].}]
      ]
    ]
    [{\textbf{Challenges}}
      [{Hallucination}
        [{Zhang et al. [53], Huang et al. [54], Rawte et al. [55], Ye et al. [56], Ji et al. [57], Tonmoy et al. [58], Jiang et al. [59].}]
      ]
      [{Bias \& Fairness}
        [{Gallegos et al. [60], Kotek et al. [61], Li et al. [62].}]
      ]
      [{Explainability}
        [{Zhao et al. [63].}]
      ]
      [{Security}
        [{Yao et al. [64], Shayegani et al. [65], Neel and Chang [66], Smith et al. [67], Dong et al. [68], Das et al. [69].}]
      ]
    ]
  ]
\end{forest}
\end{document}
